Open-Set Domain Adaptation through Self-Supervision

### 2022-02-13 paper/main.tex
Implementation fixes and minor fixes

To wrap up, our \textbf{main contributions} are: 
\begin{enumerate}
  \item we define a new method to tackle OSDA problems which exploits the rotation recognition task to perform both the known/unknown target separation
and the domain adaptation;
  \item we introduce a new OSDA metric which properly balances the measure of both the performance on predicting the known classes and the performance on doing the unknown rejection;
  \item we conduct an extensive ablation over the hyper-parameters for different variants of the self-supervised task underlying the benefits of some techniques over others.
\end{enumerate}

@@

In this step,
having separated the target into a known part $\mathcal{D}_t^{knw}$,
and an unknown part $\mathcal{D}_t^{unk}$,
we arrange two new datasets in order to perform the domain alignment while also learning
the unknown class.
The first one is $\mathcal{D}_s^*$, composed as $\mathcal{D}_s \cup \mathcal{D}_t^{unk}$,
which contains the original source images plus the target images identified as unknown classes.
We thus set the labels for $\mathcal{D}_t^{unk}$ as the class {\it unknown}.
The second one is $\mathcal{D}_t^{knw}$, which can be used to perform the domain alignment
without the risk of negative transfer.
While the feature extractor $E$ is inherited from the previous stage and leverages the previous training phase,
we also use two new classifiers,
$C_2$ and $R_2$.
They are similar to the previous classifiers but they have two important differences.
$C_2$ now has a $(|\mathcal{C}_s|+1)$-dimensional output to accomodate also the unknown class predictions and also
benefits from the previous learning,
while $R_2$ is always a single-head rotation classifier and starts the learning from scratch.
The training phase is the same as before with the difference that we do not have the center loss this time.
We also employ a different hyper-parameter $\alpha_2$ to weigh the rotation classifier loss contribution.
The objective function is again $\mathcal{L}_2 = \mathcal{L}_{C_2} + \mathcal{L}_{R_2}$,
where the two contributions are identical to equations \ref{eq:baseloss_class} and \ref{eq:baseloss_rot}.
We report the $\mathcal{L}_{R_2}$ loss contribution to make clear the usage of $\alpha_2$ and we
recall that $\mathcal{L}_{C_2}$ is now computed using the new arranged dataset $\mathcal{D}_s^*$.

@@

As we have already seen in section \ref{sec:method}, the network is composed of a feature extractor $E$, and two heads, $C_{1/2}$ and $R_{1/2}$.
For the feature extraction, we employ a ResNet-18\cite{ResNet18} pre-trained on ImageNet.
All the experiments are run training with a batch size equals to 32 and using a stochastic gradient descent optimization strategy
with a weight decay of 0.0005 and a momentum of 0.9.
The learning rate is set to 0.001 in the cases where we use a single-head rotation classifier as $R_1$, and 0.003 in the multi-head case.
The reason of this choice lies on the fact that, with a multi-head rotation classifier, we have to train 45 heads instead of a single one,
so the training process needs to be speeded up.
Moreover, we set a learning rate 10 times lower for the feature extractor weights.
We also decrease the learning rate using a step learning rate scheduler, which reduces it by a factor of 10 after 90\% of total epochs.
All models are trained for 50 epochs for the step one and for 25 epochs for the step two.
For models using the center loss a centroid learning rate of 0.001 is used.
The other hyper-parameters are analyzed performing an ablation on appendix \ref{sec:tables}.

@@

{\it Classifier $R_1$, $R_2$}: 
they are composed by a linear layer $1024\to 256$, followed by a batch normalization layer and a leaky relu activation.
The last layer is then a linear one for the actual classification $256\to 4$.
The 256-dimensional output are the features used by the center loss for inferring class centroids.
$R_2$ is always a single-head classifier, even if using a multi-head rotation classifier.

\subsection{Results}
\label{sec:results}
\begin{figure}[!htb]
  \centering
  \begin{subfigure}[!htb]{0.35\textwidth}
    \includegraphics[trim=0 0 0 2cm, clip, width=\linewidth]{hos-a1.png}
  \end{subfigure}
  \begin{subfigure}[!htb]{0.35\textwidth}
    \includegraphics[trim=0 0 0 2cm, clip, width=\linewidth]{hos-a2.png}
  \end{subfigure}
  \begin{subfigure}[!htb]{0.35\textwidth}
    \includegraphics[trim=0 0 0 2cm, clip, width=\linewidth]{hos-l.png}
  \end{subfigure}
  \begin{subfigure}[!htb]{0.35\textwidth}
    \includegraphics[trim=0 0 0 2cm, clip, width=\linewidth]{hos-th.png}
  \end{subfigure}
  \caption{\centering\label{fig:hyperparams} HOS values for different hyper-parameters. For full details see appendix \ref{sec:tables}}
\end{figure}

@@

\subsection{Ablation Study}
\label{sec:ablation_study}
Image \ref{fig:hyperparams} summarizes the parameter optimization process where a sequential approach is followed.
For each configuration one hyper-parameter is optimized at a time,
following the order
$\alpha_1$, $\lambda_1$, $\mathcal{\tilde N}$, $\alpha_2$ and picking the parameter giving the highest HOS.
Models not using center loss just skip the $\lambda_1$ optimization.
Ablation study were run and averaged on two domain shifts, 
Art $\to$ Clipart and Product $\to$ Clipart.
In appendix \ref{sec:tables} tables \ref{tab:ablationoffoff}, \ref{tab:ablationonoff} and \ref{tab:ablationonon} report all the steps followed for each configuration.
This information is also summarized in figure \ref{fig:hyperparams}.
We can notice that most of the optimal parameters are shared between configurations,
an exception being the normality score $\mathcal{\tilde N}$ on a single-headed configuration.
This is due to the fact that having to use only one head for all classes it is better to be very confident about classifying a sample as known.
Smaller $\alpha_1$ and $\alpha_2$ values are preferred as they avoid overfitting the rotation classifiers as the object classifiers take a longer time to converge.
As center loss contributions are directly summed to the rotation classifier loss term while being much bigger, 
much smaller values need to be used for a correct model convergence.

@@

The results show that self-supervision technique can help in domain adaptation task and open-set classification tasks,
but some critical points still remain in our method of study and proposed solution.
The most important one is probably the parameter optimization method for different models,
as small variations can cause huge differences in results sequentially optimizing hyper-parameters is a sub-optimal heuristic.
Furthermore,
having models learn different tasks simultaneosly can lead to instability, 
so using slower learning models at the expense of longer training times can improve results.
A criticality is represented by the normality score hyper-parameter:
model confidence over accepting or rejecting a sample is very thight between known and unknwon samples,
so a better function do have more spread scores can bring more efficient separation,
ultimately resulting in a better quality input data in the second step.
Last,
center loss function relies on learning centroids based on sample features to predict rotation.
This formulation requires picking a specific learning rate for such centroids,
but we didn't run any test on how such learning rate impacts predictions or sample separability.

@@

This section contains tables \ref{tab:ablationoffoff}, \ref{tab:ablationonoff} and \ref{tab:ablationonon} report the hyper-parameters optimization sequence, while tables \ref{tab:results} report the final values for each domain shift with the chosen hyper-parameters.

\begin{table}[h!]
  \centering
  \begin{tabular}[h]{||c|c|c||c||}
    \hline
    \multicolumn{4}{||c||}{OFF-OFF} \\
    \hline
    $\alpha_1$ & $\mathcal{\tilde N}$ & $\alpha_2$ & HOS$_{mean}$\\    
    \hline
    \hline
    \multicolumn{4}{||c||}{Picking $\alpha_1$} \\
    \hline
    {\bf 1.0}  & \multirow{4}{*}{0.6} & \multirow{4}{*}{3.0} & {\bf 40.27\%} \\
    3.0  & & & 22.69\% \\
    5.0  & & & 18.78\% \\
    10.0 & & & 9.99\% \\
    \hline
    \hline
    \multicolumn{4}{||c||}{Picking $\mathcal{\tilde N}$} \\
    \hline
    \multirow{6}{*}{1.0} & 0.50 & \multirow{6}{*}{3.0}  & 28.05\%\\
    & 0.55 & & 34.73\% \\
    & 0.60 & & 40.27\% \\
    & 0.65 & & 43.16\% \\
    & {\bf 0.70} & & {\bf 44.38\%} \\
    & 0.75 & & 43.87\% \\
    \hline
    \hline
    \multicolumn{4}{||c||}{Picking $\alpha_2$} \\
    \hline
    \multirow{7}{*}{1.0} & \multirow{7}{*}{0.7} & 0.1 & 42.79\%\\
    && 1.0 & 44.35\% \\
    && 2.0 & 43.53\% \\
    && {\bf 3.0} & {\bf 44.38}\% \\
    && 4.0 & 43.12\% \\
    && 5.0 & 41.97\% \\
    && 10.0 & 42.01\% \\
    \hline
  \end{tabular}
  \caption{\centering\label{tab:ablationoffoff} Hyper-parametr optimization process for configuration Multi-Head Off and Center-Loss Off}
\end{table}

\begin{table}[t!]
  \vspace{-2cm}
  \centering
  \begin{tabular}[h]{||c|c|c||c||}
    \hline
    \multicolumn{4}{||c||}{ON-OFF} \\
    \hline
    $\alpha_1$ & $\mathcal{\tilde N}$ & $\alpha_2$ & HOS$_{mean}$\\    
    \hline
    \hline
    \multicolumn{4}{||c||}{Picking $\alpha_1$} \\
    \hline
    {\bf 1.0}  & \multirow{4}{*}{0.6} & \multirow{4}{*}{3.0} & {\bf 43.48\%} \\
    3.0  & & & 38.45\% \\
    5.0  & & & 37.61\% \\
    10.0 & & & 33.23\% \\
    \hline
    \hline
    \multicolumn{4}{||c||}{Picking $\mathcal{\tilde N}$} \\
    \hline
    \multirow{6}{*}{1.0} & 0.4 & \multirow{6}{*}{3.0}  & 38.40\%\\
    & 0.45 & & 42.40\% \\
    & 0.5 & & 43.48\% \\
    & 0.55 & & 46.21\% \\
    & {\bf0.6} & & {\bf 50.17\%} \\
    & 0.65 & & 45.82\% \\
    \hline
    \hline
    \multicolumn{4}{||c||}{Picking $\alpha_2$} \\
    \hline
    \multirow{7}{*}{1.0} & \multirow{7}{*}{0.7} & 0.1 & 46.02\%\\
    && 1.0 & 47.71\% \\
    && 2.0 & 46.56\% \\
    && {\bf 3.0} & {\bf 50.17\%} \\
    && 4.0 & 46.57\% \\
    && 5.0 & 47.52\% \\
    && 10.0 & 44.56\% \\
    \hline
  \end{tabular}
  \caption{\centering\label{tab:ablationonoff} Hyper-parameters optimization process for configuration Multi-Head On and Center-Loss Off}
\end{table}

\begin{table}[b!]
  \centering
  \begin{tabular}[h]{||c|c|c|c||c||}
    \hline
    \multicolumn{5}{||c||}{ON-ON} \\
    \hline
    $\alpha_1$ & $\lambda_1$ & $\mathcal{\tilde N}$ & $\alpha_2$ & HOS$_{mean}$ \\
    \hline
    \hline
    \multicolumn{5}{||c||}{Picking $\alpha_1$} \\
    \hline
    1.0 & \multirow{4}{*}{0.01} & \multirow{4}{*}{0.05} & \multirow{4}{*}{3.0} & 44.90\% \\
    {\bf 3.0} & && & {\bf 45.33\%} \\
    5.0 & && & 42.41\% \\
    10.0 & && & 37.15\% \\
    \hline
    \hline
    \multicolumn{5}{||c||}{Picking $\lambda_1$} \\
    \hline
    \multirow{5}{*}{3} & 0.0001 & \multirow{5}{*}{0.5} & \multirow{5}{*}{3.0} & 39.90\% \\
    & 0.001 & & & 36.71\% \\
    & 0.01 & & & 45.33\% \\
    & {\bf 0.05 }& & & {\bf 46.63\%} \\
    & 0.1 & & & 37.44\% \\
    \hline
    \hline
    \multicolumn{5}{||c||}{Picking $\mathcal{\tilde N}$} \\
    \hline
    \multirow{5}{*}{3} & \multirow{5}{*}{0.05} & 0.4 & \multirow{5}{*}{3.0} & 44.32\% \\
    & & 0.45 & & 45.13\% \\
    & & 0.5 & & 46.63\% \\
    & & 0.55 & & 47.09\% \\
    & & {\bf 0.6} & & {\bf 49.78\%} \\
    & & 0.65 & & 47.23\% \\
    \hline
    \hline
    \multicolumn{5}{||c||}{Picking $\alpha_2$} \\
    \hline
    \multirow{7}{*}{3} & \multirow{7}{*}{0.05} & \multirow{7}{*}{0.6} & 0.1 & 45.73\% \\
    & & & 1.0 & 45.23\% \\
    & & & 2.0 & 45.76\% \\
    & & & {\bf 3.0} & {\bf 49.78\%} \\
    & & & 4.0 & 46.20\% \\
    & & & 5.0 & 48.60\% \\
    & & & 10.0 & 44.14\% \\
    \hline
  \end{tabular}
  \caption{\centering\label{tab:ablationonon} Hyper-parameters optimization process for configuration Multi-Head On and Center-Loss On}
\end{table}

>>>>

To wrap up, our \textbf{main contributions} are: 
\begin{enumerate}
  \item we define a new method to tackle OSDA problems which exploits the rotation recognition task to perform both the known/unknown target separation
and the domain adaptation;
  \item we introduce a new OSDA metric which properly balances the measure of both the performance on predicting the known classes and the performance on doing the unknown rejection;
  \item we conduct an extensive ablation over the hyperparameters for different variants of the self-supervised task underlying the benefits of some techniques over others.
\end{enumerate}

@@

In this step,
having separated the target into a known part $\mathcal{D}_t^{knw}$,
and an unknown part $\mathcal{D}_t^{unk}$,
we arrange two new datasets in order to perform the domain alignment while also learning
the unknown class.
The first one is $\mathcal{D}_s^*$, composed as $\mathcal{D}_s \cup \mathcal{D}_t^{unk}$,
which contains the original source images plus the target images identified as unknown classes.
We thus set the labels for $\mathcal{D}_t^{unk}$ as the class {\it unknown}.
The second one is $\mathcal{D}_t^{knw}$, which can be used to perform the domain alignment
without the risk of negative transfer.
While the feature extractor $E$ is inherited from the previous stage and leverages the previous training phase,
we also use two new classifiers,
$C_2$ and $R_2$.
They are similar to the previous classifiers but they have two important differences.
$C_2$ now has a $(|\mathcal{C}_s|+1)$-dimensional output to accomodate also the unknown class predictions and also
benefits from the previous learning,
while $R_2$ is always a single-head rotation classifier and starts the learning from scratch.
The training phase is the same as before with the difference that we do not have the center loss this time.
We also employ a different hyperparameter $\alpha_2$ to weigh the rotation classifier loss contribution.
The objective function is again $\mathcal{L}_2 = \mathcal{L}_{C_2} + \mathcal{L}_{R_2}$,
where the two contributions are identical to equations \ref{eq:baseloss_class} and \ref{eq:baseloss_rot}.
We report the $\mathcal{L}_{R_2}$ loss contribution to make clear the usage of $\alpha_2$ and we
recall that $\mathcal{L}_{C_2}$ is now computed using the new arranged dataset $\mathcal{D}_s^*$.

@@

As we have already seen in section \ref{sec:method}, the network is composed of a feature extractor $E$, and two heads, $C_{1/2}$ and $R_{1/2}$.
For the feature extraction, we employ a ResNet-18\cite{ResNet18} pre-trained on ImageNet.
All the experiments are run training with a batch size equals to 32 and using a stochastic gradient descent optimization strategy
with a weight decay of 0.0005 and a momentum of 0.9.
The learning rate is set to 0.001 in the cases where we use a single-head rotation classifier as $R_1$, and 0.003 in the multi-head case.
The reason of this choice lies on the fact that, with a multi-head rotation classifier, we have to train 45 heads instead of a single one,
so the training process needs to be speeded up.
Moreover, we set a learning rate 10 times lower for the weights of the feature extractor and $C_{1/2}$.
We also decrease the learning rate using a step learning rate scheduler, which reduces it by a factor of 10 after 90\% of total epochs.
All models are trained for 50 epochs for the step one and for 25 epochs for the step two.
For models using the center loss a centroid learning rate of 0.001 is used.
The other hyperparameters are analyzed performing an ablation on them,
details can be found on the section \ref{sec:ablation_study} and the results of the ablation are
reported on appendix \ref{sec:tables}.

@@

{\it Classifier $R_1$, $R_2$}: 
they are seen as discriminators composed by a linear layer $1024\to 256$,
followed by a batch normalization layer and a leaky relu activation.
The last layer is then a linear one for the actual classification $256\to 4$.
In the case of multi-head rotation classifier,
the discriminator is then composed of $|\mathcal{C}_s|$ different linear layers, both for the first and the last one.
Moreover, the 256-dimensional output are the features used by the center loss for inferring class centroids.
$R_2$ is always a single-head classifier, even if using a multi-head rotation classifier.

\subsection{Results}
\label{sec:results}
\begin{figure}[!htb]
  \centering
  \begin{subfigure}[!htb]{0.35\textwidth}
    \includegraphics[trim=0 0 0 2cm, clip, width=\linewidth]{hos-a1.png}
  \end{subfigure}
  \begin{subfigure}[!htb]{0.35\textwidth}
    \includegraphics[trim=0 0 0 2cm, clip, width=\linewidth]{hos-a2.png}
  \end{subfigure}
  \begin{subfigure}[!htb]{0.35\textwidth}
    \includegraphics[trim=0 0 0 2cm, clip, width=\linewidth]{hos-l.png}
  \end{subfigure}
  \begin{subfigure}[!htb]{0.35\textwidth}
    \includegraphics[trim=0 0 0 2cm, clip, width=\linewidth]{hos-th.png}
  \end{subfigure}
  \caption{\centering\label{fig:hyperparams} HOS values for different hyperparameters. For full details see appendix \ref{sec:tables}}
\end{figure}

@@

\subsection{Ablation Study}
\label{sec:ablation_study}
Image \ref{fig:hyperparams} summarizes the parameter optimization process where a sequential approach is followed.
For each configuration one hyperparameter is optimized at a time,
following the order
$\alpha_1$, $\lambda_1$, $\mathcal{\tilde N}$, $\alpha_2$ and picking the parameter giving the highest HOS.
Models not using center loss just skip the $\lambda_1$ optimization.
Ablation study were run and averaged on two domain shifts, 
Art $\to$ Clipart and Product $\to$ Clipart.
In appendix \ref{sec:tables} tables \ref{tab:ablationoffoff}, \ref{tab:ablationonoff} and \ref{tab:ablationonon} report all the steps followed for each configuration.
This information is also summarized in figure \ref{fig:hyperparams}.
We can notice that most of the optimal parameters are shared between configurations,
an exception being the normality score $\mathcal{\tilde N}$ on a single-headed configuration.
This is due to the fact that having to use only one head for all classes it is better to be very confident about classifying a sample as known.
Smaller $\alpha_1$ and $\alpha_2$ values are preferred as they avoid overfitting the rotation classifiers as the object classifiers take a longer time to converge.
As center loss contributions are directly summed to the rotation classifier loss term while being much bigger, 
much smaller values need to be used for a correct model convergence.

@@

The results show that self-supervision technique can help in domain adaptation task and open-set classification tasks,
but some critical points still remain in our method of study and proposed solution.
The most important one is probably the parameter optimization method for different models,
as small variations can cause huge differences in results sequentially optimizing hyperparameters is a sub-optimal heuristic.
Furthermore,
having models learn different tasks simultaneosly can lead to instability, 
so using slower learning models at the expense of longer training times can improve results.
A criticality is represented by the normality score hyperparameter:
model confidence over accepting or rejecting a sample is very thight between known and unknwon samples,
so a better function do have more spread scores can bring more efficient separation,
ultimately resulting in a better quality input data in the second step.
Last,
center loss function relies on learning centroids based on sample features to predict rotation.
This formulation requires picking a specific learning rate for such centroids,
but we didn't run any test on how such learning rate impacts predictions or sample separability.

@@

This section contains tables \ref{tab:ablationoffoff}, \ref{tab:ablationonoff} and \ref{tab:ablationonon} report the hyperparameters optimization sequence, while tables \ref{tab:results} report the final values for each domain shift with the chosen hyperparameters.

\begin{table}[h!]
  \centering
  \begin{tabular}[h]{||c|c|c||c||}
    \hline
    \multicolumn{4}{||c||}{OFF-OFF} \\
    \hline
    $\alpha_1$ & $\mathcal{\tilde N}$ & $\alpha_2$ & HOS$_{mean}$\\    
    \hline
    \hline
    \multicolumn{4}{||c||}{Picking $\alpha_1$} \\
    \hline
    {\bf 1.0}  & \multirow{4}{*}{0.6} & \multirow{4}{*}{3.0} & {\bf 40.27\%} \\
    3.0  & & & 22.69\% \\
    5.0  & & & 18.78\% \\
    10.0 & & & 9.99\% \\
    \hline
    \hline
    \multicolumn{4}{||c||}{Picking $\mathcal{\tilde N}$} \\
    \hline
    \multirow{6}{*}{1.0} & 0.50 & \multirow{6}{*}{3.0}  & 28.05\%\\
    & 0.55 & & 34.73\% \\
    & 0.60 & & 40.27\% \\
    & 0.65 & & 43.16\% \\
    & {\bf 0.70} & & {\bf 44.38\%} \\
    & 0.75 & & 43.87\% \\
    \hline
    \hline
    \multicolumn{4}{||c||}{Picking $\alpha_2$} \\
    \hline
    \multirow{7}{*}{1.0} & \multirow{7}{*}{0.7} & 0.1 & 42.79\%\\
    && 1.0 & 44.35\% \\
    && 2.0 & 43.53\% \\
    && {\bf 3.0} & {\bf 44.38}\% \\
    && 4.0 & 43.12\% \\
    && 5.0 & 41.97\% \\
    && 10.0 & 42.01\% \\
    \hline
  \end{tabular}
  \caption{\centering\label{tab:ablationoffoff} Hyperparametr optimization process for configuration Multi-Head Off and Center-Loss Off}
\end{table}

\begin{table}[t!]
  \vspace{-2cm}
  \centering
  \begin{tabular}[h]{||c|c|c||c||}
    \hline
    \multicolumn{4}{||c||}{ON-OFF} \\
    \hline
    $\alpha_1$ & $\mathcal{\tilde N}$ & $\alpha_2$ & HOS$_{mean}$\\    
    \hline
    \hline
    \multicolumn{4}{||c||}{Picking $\alpha_1$} \\
    \hline
    {\bf 1.0}  & \multirow{4}{*}{0.6} & \multirow{4}{*}{3.0} & {\bf 43.48\%} \\
    3.0  & & & 38.45\% \\
    5.0  & & & 37.61\% \\
    10.0 & & & 33.23\% \\
    \hline
    \hline
    \multicolumn{4}{||c||}{Picking $\mathcal{\tilde N}$} \\
    \hline
    \multirow{6}{*}{1.0} & 0.4 & \multirow{6}{*}{3.0}  & 38.40\%\\
    & 0.45 & & 42.40\% \\
    & 0.5 & & 43.48\% \\
    & 0.55 & & 46.21\% \\
    & {\bf0.6} & & {\bf 50.17\%} \\
    & 0.65 & & 45.82\% \\
    \hline
    \hline
    \multicolumn{4}{||c||}{Picking $\alpha_2$} \\
    \hline
    \multirow{7}{*}{1.0} & \multirow{7}{*}{0.7} & 0.1 & 46.02\%\\
    && 1.0 & 47.71\% \\
    && 2.0 & 46.56\% \\
    && {\bf 3.0} & {\bf 50.17\%} \\
    && 4.0 & 46.57\% \\
    && 5.0 & 47.52\% \\
    && 10.0 & 44.56\% \\
    \hline
  \end{tabular}
  \caption{\centering\label{tab:ablationonoff} Hyperparameters optimization process for configuration Multi-Head On and Center-Loss Off}
\end{table}

\begin{table}[b!]
  \centering
  \begin{tabular}[h]{||c|c|c|c||c||}
    \hline
    \multicolumn{5}{||c||}{ON-ON} \\
    \hline
    $\alpha_1$ & $\lambda_1$ & $\mathcal{\tilde N}$ & $\alpha_2$ & HOS$_{mean}$ \\
    \hline
    \hline
    \multicolumn{5}{||c||}{Picking $\alpha_1$} \\
    \hline
    1.0 & \multirow{4}{*}{0.01} & \multirow{4}{*}{0.05} & \multirow{4}{*}{3.0} & 44.90\% \\
    {\bf 3.0} & && & {\bf 45.33\%} \\
    5.0 & && & 42.41\% \\
    10.0 & && & 37.15\% \\
    \hline
    \hline
    \multicolumn{5}{||c||}{Picking $\lambda_1$} \\
    \hline
    \multirow{5}{*}{3} & 0.0001 & \multirow{5}{*}{0.5} & \multirow{5}{*}{3.0} & 39.90\% \\
    & 0.001 & & & 36.71\% \\
    & 0.01 & & & 45.33\% \\
    & {\bf 0.05 }& & & {\bf 46.63\%} \\
    & 0.1 & & & 37.44\% \\
    \hline
    \hline
    \multicolumn{5}{||c||}{Picking $\mathcal{\tilde N}$} \\
    \hline
    \multirow{5}{*}{3} & \multirow{5}{*}{0.05} & 0.4 & \multirow{5}{*}{3.0} & 44.32\% \\
    & & 0.45 & & 45.13\% \\
    & & 0.5 & & 46.63\% \\
    & & 0.55 & & 47.09\% \\
    & & {\bf 0.6} & & {\bf 49.78\%} \\
    & & 0.65 & & 47.23\% \\
    \hline
    \hline
    \multicolumn{5}{||c||}{Picking $\alpha_2$} \\
    \hline
    \multirow{7}{*}{3} & \multirow{7}{*}{0.05} & \multirow{7}{*}{0.6} & 0.1 & 45.73\% \\
    & & & 1.0 & 45.23\% \\
    & & & 2.0 & 45.76\% \\
    & & & {\bf 3.0} & {\bf 49.78\%} \\
    & & & 4.0 & 46.20\% \\
    & & & 5.0 & 48.60\% \\
    & & & 10.0 & 44.14\% \\
    \hline
  \end{tabular}
  \caption{\centering\label{tab:ablationonon} Hyperparameters optimization process for configuration Multi-Head On and Center-Loss On}
\end{table}
